\documentclass[margin,line]{res}
\usepackage[hidelinks]{hyperref}
\usepackage{color}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{DHRUV KUMAR\vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
9/134, Bagh Muzaffar Khan         & {\it Mobile:}  (91) 819-780-1366 \\            
 Agra, Uttar Pradesh, & {\it E-mail:}  \href{mailto:gargdhruv36@gmail.com }{gargdhruv36@gmail.com }\\
 India - 282002 &{\it URL:}  \href{http://kudhru.github.io}{\bf kudhru.github.io}
% {\it Skype id:}  gargdhruv36@hotmail.com\\
% &  {\it Personal webpage:} \href{http://www.dhruvkumar.me}{\bf www.dhruvkumar.me}\\
\end{tabular}


\section{\sc Research Interests}
Data Mining, Natural Language Processing, Artificial Intelligence, High Performance Computing.

\section{\sc Education}
{\bf Birla Institute of Technology and Science} (BITS), Pilani, India \hfill {\bf {Aug 2010 - May 2014}}\\
%\vspace*{-.3cm}
{\em Bachelor of Engineering (Hons.) Computer Science }
\vspace*{.3cm}
\begin{list2}
\item CGPA:  {\bf {9.92 / 10.0}}
\item {\bf Rank 1} in Class of 2014 of Computer Science, comprising of 120 students. 
\item {\bf Rank 3} in Class of 2014 of BITS-Pilani, comprising of 800 students.
%\vspace*{.3cm}
\item {\bf Relevant Courses}: Discrete Structures, Microprocessor Programming
and Interface, Data Structures and Algorithms, Theory of Computation, Digital Electronics,
Computer Organization, Operating Systems, Database Systems, Computer Networks,
Programming Languages, Compiler Construction, Computer Graphics, Advanced Data Mining, Machine Learning.

\end{list2}


\section{\sc Research Experience}

%{\bf Argonne National Laboratory, USA}

%\vspace{-.3cm}
%{\em Mentor: Pavan Balaji} \hfill {\bf August, 2016 - Present}\\
%Implementation of Unbalanced Tree Search (UTS) using MPI two-sided communication and MPI RMA.

{\bf ADAPT Lab, BITS-Pilani}\hfill {\bf Apr, 2013 - Oct, 2014}\\
%\vspace{-.3cm}
{\em {\bf Project:} A New Distributed Computing Framework for Data Mining} \\
{\em {\bf Mentors:} Navneet Goyal, Poonam Goyal, Sundar Balasubramaniam}
\vspace{.3cm}
\begin{list2}
\item Designed and implemented data mining algorithms such as OPTICS, SLINK, DBSCAN for shared memory and
distributed memory models.
\item Used data distribution and task parallelism techniques for exploiting multicore and multinode
architectures. Implemented using OpenMP and OpenMPI libraries in C.
\item The work resulted in a number of publications. (See below)
\end{list2}

\section{\sc Publications}
Poonam Goyal, Jagat Sesh Challa, {\bf Dhruv Kumar}, Navneet Goyal, Sundar Balasubramaniam.
{\it Grid-R-tree: A data structure for efficient neighborhood and nearest neighbor queries in
data mining}, submitted for review in Journal of Data \& Knowledge Engineering, Elsevier.\href{https://drive.google.com/open?id=0B5R2WFoF983oN2dCcDJfaE9nVHM}{\color{blue}[Link]}

{\bf Dhruv Kumar}, Poonam Goyal, Navneet Goyal. {\it An Efficient method for Batch Updates in OPTICS Cluster Ordering}, to appear in International Journal of Data Analysis Techniques and
Strategies.\href{https://drive.google.com/open?id=0B5R2WFoF983oUmRrTWlBeWlQNWs}{\color{blue}[Link]}

Poonam Goyal, Sonal Kumari, Ankit Sood, {\bf  Dhruv Kumar}, Sundar Balasubramaniam, and Navneet
Goyal. {\it Exact, Fast and Scalable Parallel DBSCAN for Commodity Platforms}, to appear in International Conference on Distributed Computing and Networking
(ICDCN), 2017.\href{https://drive.google.com/open?id=0B5R2WFoF983oWEtOVUNCS3FUZ1E}{\color{blue}[Link]}

Poonam Goyal, Sonal Kumari, Sumit Sharma, {\bf Dhruv Kumar}, Vivek Kishore, Sundar
Balasubramaniam, and Navneet Goyal. {\it A fast, Scalable SLINK Algorithm for Commodity
Cluster Computing Exploiting Spatial Locality}, to appear in IEEE International Conference on High Performance Computing and Communications (HPCC), 2016.\href{https://drive.google.com/open?id=0B5R2WFoF983obUlHLTBTTmxsMzA}{\color{blue}[Link]}

Poonam Goyal, Sonal Kumari, {\bf Dhruv Kumar}, Sundar Balasubramaniam, Navneet Goyal, Saiyedul
Islam, and Jagat Sesh Challa. {\it Parallelizing OPTICS for Commodity Clusters} in International Conference on Distributed Computing and Networking (ICDCN), 2015.\href{http://dl.acm.org/citation.cfm?id=2684477}{\color{blue}[Link]}

Poonam Goyal, Sonal Kumari, {\bf Dhruv Kumar}, Sundar Balasubramaniam, and Navneet Goyal.  
{\it Parallelizing OPTICS for multicore systems} in ACM India Computing
Conference (ACM COMPUTE), 2014.\href{http://dl.acm.org/citation.cfm?id=2675763}{\color{blue}[Link]}

\section{\sc Professional Experience}

%{\bf Argonne National Laboratory, USA}

%\vspace{-.3cm}
%{\em Mentor: Pavan Balaji} \hfill {\bf August, 2016 - Present}\\
%Implementation of Unbalanced Tree Search (UTS) using MPI two-sided communication and MPI RMA.

{\bf \href{www.primarykey.io}{primarykey.io} and \href{www.corporatecabs.io}{corporatecabs.io}} \hfill {\bf Apr, 2016 - Current}\\
%\vspace{-.3cm}
{\em Co-founder and Chief Technology Officer}
\vspace{.3cm}
\begin{list2}
\item Designed and implemented the entire back-end for \href{www.primarykey.io}{\bf \color{blue}{primarykey.io}} and \href{www.corporatecabs.io}{\bf \color{blue} {corporatecabs.io}} from scratch.
\item The entire back-end functionality was exposed using RESTful APIs implemented using Django web framework and hosted using Amazon web services.
\item Gained valuable experience in building scalable and secure back-ends for web and mobile applications.
\end{list2}

{\bf Goldman Sachs, Bengaluru, India} \hfill {\bf Nov, 2014 - Apr, 2016}\\
%\vspace{-.4cm}
{\em Software Developer, Investment Management Division}
\vspace{.3cm}
\begin{list2}
\item Improved the efficiency of risk-management system by suggesting improvements to the SQL
queries going to Sybase IQ database.
\item Assisted in migrating from Sybase IQ database to MemSQL database for faster access.
\item Wrote APIs for accessing MemSQL database.
\item Implemented a H2-database based server for allowing real-time updates to the tables residing in
the servers.
\item Learnt about the real life use-cases of databases.
\end{list2}

{\bf CSIR-CEERI, Pilani, India}\hfill {\bf May, 2012 - July, 2012}\\
%\vspace{-.3cm}
{\em Summer Intern} 
\vspace{.3cm}
\begin{list2}
\item Studied, compared and implemented various unsupervised machine learning algorithms.
\item Learnt about the use of these algorithms in real world applications
\end{list2}

\section{\sc Selected Academic Projects}

{\bf Restaurant Recommender System} \hfill {\bf Oct, 2013 - Nov, 2013}\\

\vspace{-.3cm}
\begin{list2}
\item An application which can recommend suitable restaurants based on user inputs of location, type of
cuisine, type of meal, etc.
\item Restaurant reviews taken from yelp.com and processed using NLP techniques.
\end{list2}

{\bf Complier Construction for a “Toy” Language} \hfill {\bf Jan, 2013 - Apr, 2013}\\

\vspace{-.3cm}
\begin{list2}
\item Designed lexical, syntax, semantic, code generation phases of compiler in C.
\item Efficient use of Hash Tables for constructing symbol tables.
\item Designed Abstract syntax tree rules for semantic analysis.
\end{list2}

{\bf Transcripts Website for BITS, Pilani} \hfill {\bf Feb, 2012 - Aug, 2013}\\

\vspace{-.3cm}
\begin{list2}
\item Used by BITS students and alumni for the application of Duplicate Transcripts and Grade Sheets.
\item Built using ASP.NET, C\#.NET, Microsoft Visual Studio, MS SQL Server.
\end{list2}




\section{\sc Technical Skills} 
\begin{list2}

\item {\bf Programming:} C, Java, Python, OpenMPI, OpenMP, MySQL, Verilog, Matlab
\item {\bf Mobile and Web Technologies:} HTML, CSS, JavaScript, AngularJS, Django, Android
\item {\bf Cloud platforms:} Amazon web services
\end{list2}
 



\section{\sc Honors and Awards}
\begin{list2}
\item Awarded merit scholarship of total worth Rs 4,75,000 for being in top 10 students among 800 students of BITS, Pilani by the institute. {\bf [Aug, 2010 - May, 2014]}

\item Awarded research incentive fellowship of Rs 25,000 in recognition of the contribution in the
undergraduate thesis project. {\bf [May, 2014]}

\item Nominated twice for O P Jindal Engineering \& Management Scholarship. {\bf [2011, 2012]}

\item Selected for attending 4th South Asia Workshop on Research Frontiers in Computer Science at
NUS School of Computing, Singapore. {\bf [May 2014]}
\end{list2}

\end{resume}
\end{document}